Visual proteomics using whole-lamella 2D template matching

### 2022-03-02 manuscript.tex
Refine macthes + assemble [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/00311ccf9074082904cef550d9b63ff61297b3c1.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/00311ccf9074082904cef550d9b63ff61297b3c1/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1923840837

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/faafadc025e8ca90737699af9c8f5d76cfeef9a3/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/faafadc025e8ca90737699af9c8f5d76cfeef9a3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@faafadc}
on March 1, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/00311ccf9074082904cef550d9b63ff61297b3c1/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/00311ccf9074082904cef550d9b63ff61297b3c1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@00311cc}
on March 2, 2022.
